Enter our title here

### 2017-12-20 manuscript.tex
format code to fit in text boxes

\begin{figure}
\caption{This code does this}
\begin{verbatim}[frame=single]
--- type:NormalExercise lang:r xp:100 skills:1 key:9a4fea2da
## Visualizing quantitative data in R

@@

\begin{figure}
\caption{This code does this}
\begin{Verbatim}[frame=single]
--- type:PlainMultipleChoiceExercise lang:r xp:50 skills:1 key:9707072219
## Quick check 2

>>>>

\begin{figure}
\caption{This code does this}
\begin{verbatim}
--- type:NormalExercise lang:r xp:100 skills:1 key:9a4fea2da
## Visualizing quantitative data in R

@@

\begin{figure}
\caption{This code does this}
\begin{Verbatim}[frame=single]
--- type:PlainMultipleChoiceExercise lang:r xp:50 skills:1
    key:9707072219

## Quick check 2
